---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# authorlist

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/qiang-yang-ecology/authorlist.svg?branch=master)](https://travis-ci.com/qiang-yang-ecology/authorlist)
<!-- badges: end -->

The goal of authorlist is to creat the formatted author list for manuscripts with many authors. Formatting the author list and the affiliation list in Word for the manuscript with many coauthors is painful and time-consuming. However, putting the author names and affiliations together in a CSV file is easy. The package "authorlist" automatically produces a Word document with the formatted author and affiliation list ready for submission from a CSV file. The template of the CSV file, which includes the coauthors' names, affiliations, and their order in the author list, can be downloaded from https://figshare.com/articles/dataset/CSV_template_for_R_package_authorlist_/16794901. The leading author of the manuscript could make it even easier by sharing the CSV template through Dropbox or Google Drive and asking the coauthors to fill in their information. 

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("qiang-yang-ecology/authorlist")
```
## Example

This is a basic example which shows you how to produce the Word document with formatted author and affiliation list:

- step 1: download the template from the following link to your computer:
https://figshare.com/articles/dataset/CSV_template_for_R_package_authorlist_/16794901

- step2: modify the csv file to include the coauthor information of your manuscript.

- step3: produced the formatted author and affiliation list 
```{r example, eval=FALSE}
library(authorlist)
toAuthorlist(source.csv = "~/Downloads/authorlist.csv",
             # the csv including the author names and affiliations
             target = "~/Downloads/authorlist.docx",
             # where you save the produced word document
             type="numbered"
             # type of numbering the affiliations, could be numbered (numbers) or alphabeta (letters)
)
```

